### 2020-10-28 smoothing.tex
some question on suggested sigma

>>>>

Questions/Clarifications:
(1) We have two testing rates; (i) $\tau$ and (ii) $\rho$.
$\tau$ is the testing rate when $W \approx 0$ so no one is left in the untested compartments. (Here I am not sure why "a time scale $\tau$ for the maximum rate of testing the whole untested population"?).
On the other hand $\rho$ is the testing rate at the begining of the pandemic when $W \approx N_0$. The latter requires $\tau \gg \rho$. Am I thinking right here?  
(2) $\tau$ has the same dimension as $\rho$ which is testing rate, thus 1/time per capita?
(3) In the simmulation, I picked $\tau=1$. This made sense to me if the answeres to all above questions are "yes". Not sure what to pick if I was not thinking right in the above question.
